\documentclass[10.5pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{lmodern}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\renewcommand{\familydefault}{\sfdefault}

\newenvironment{shortlist}
{\setlength{\linewidth}{0.9\linewidth}
\begin{itemize}
}
{\end{itemize}}

\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

\begin{document}

\begin{center}
{\LARGE \textbf{Austin Palmer}}
\vspace{0.2em}


444 E 75th St\ \ \textbullet
\ \ Apt\ 9B\ \ \textbullet
\ \ New York, NY 10021
\\
(770) 843-3065\ \ \textbullet
\ \ acharlie1377@gmail.com
\end{center}

\hrule
\vspace{-0.4em}


\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

    \item[]
    \headerrow
        {\textbf{Columbia University}}
        {\textbf{New York, NY}}
    \\
    \headerrow
        {\emph{Teaching Assistant}}
        {\emph{Sept 2017 -- May 2021}}
    \begin{shortlist}
        \item[--]
        Designed and led recitations, graded programming-focused exams written in Python, and wrote
        automated grade-uploading scripts for a graduate-level Simulation course.
        \item[--]
        Graded and assisted students with large programming-focused projects in a graduate-level Applications Programming course, using
        Python, C$^{++}$, and VBA.
        \item[--]
        Proctored exams and led office hours to assist students struggling with class material in a graduate-level Data Analysis course.
    \end{shortlist}

    \item[]
	\headerrow
		{\textbf{Travel Tripper}}
        {\textbf{New York, NY}}
	\\
	\headerrow
		{\emph{Support Engineer}}
		{\emph{Jan 2017 -- Jul 2017}}
    \begin{shortlist}
        \item[--]
        Located and fixed bugs within a large reservation management application written in Java
        and Ruby.

        \item[--]
        Implemented and modified JavaScript tracking code for ad services such as Google Tag
        Manager and Bing Universal Event Tracking.
    \end{shortlist}

    \item[]
	\headerrow
		{\textbf{Direct Agents}}
		{\textbf{New York, NY}}
	\\
	\headerrow
		{\emph{Web Developer}}
		{\emph{Jul 2016 -- Dec 2016}}
	\begin{shortlist}
        \item[--]
        Augmented ad reporting and tracking services by developing server-side
        applications in C$^\sharp$.

        \item[--]
        Implemented multi-threaded loaders to pull and synthesize advertising data from third-party
        APIs.

	\end{shortlist}

    \item[]
	\headerrow
		{\textbf{Haver Analytics}}
		{\textbf{New York, NY}}
	\\
	\headerrow
		{\emph{Research Assistant}}
		{\emph{Jun 2016 -- Feb 2017}}
	\begin{shortlist}
        \item[--]
        Analyzed, updated, and maintained economic data for countries in eastern Europe.
        \item[--]
        Improved versatility of databases by adding new economic series and revising historical data, and
        generating seasonal- and trend-adjusted data.
        \item[--]
        Increased productivity and efficiency by automating database 
        updates and writing low-level web scraping scripts.
	\end{shortlist}

\end{itemize}

\hrule
\vspace{-0.4em}

\subsection*{Projects}
\hyphenpenalty 10000

\begin{itemize}
    \parskip=0.1em

    \item[]
	\headerrow
		{\textbf{Factorus}}
		{}
	\begin{shortlist}
        \item[--]
        General refactoring tool for the Vim text editor, written entirely in Vimscript.
        \item[--]
        Supports context-aware renaming of objects, parameter addition, and variable encapsulation in C, C$^++$, and Java, as well as an automatic 
        method-extraction tool.
        \item[--]
        Supports limited object renaming and method extraction in Python.
    \end{shortlist}

\end{itemize}

\hrule
\vspace{-0.4em}

\subsection*{Education}

\hyphenpenalty 10000
\begin{itemize}
	\parskip=0.1em

    \item[]
    \headerrow
        {\textbf{MS, Operations Research}}
        {\textbf{Sept 2017 -- May 2018}}
    \\
    \headerrow
        {\emph{Columbia University, IEOR}}
        {\emph{New York, NY}}

    \item[] 
	\headerrow
        {\textbf{BA, Mathematics \& Economics}}
		{\textbf{Sept 2014 -- Dec 2016}}
	\\
	\headerrow
        {\emph{New York University, College of Arts \& Sciences}}
		{\emph{New York, NY}}


\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Skills}

\hyphenpenalty=1000
\begin{itemize*}
    \item[]
    \textbf{Languages/Frameworks: }C, C$^\sharp$, Entity Framework, Hibernate, Java, PHP, Python, Spring Framework, Struts, SQL
    \vspace{0.2em}

    \item[]
    \textbf{Technical Skills: }Ant, Bash, Git, \LaTeX, Linux, MVC, OOP, Vim

    \vspace{0.2em}

    \item[]
    \textbf{Web Development: }Angular, Apache Tomcat, ASP.NET, HTML/CSS, JavaScript/JQuery
    \vspace{0.2em}

\end{itemize*}

\end{document}
